### 2016-05-03 forgerard.tex
fix redefinition of gamma_1

\begin{document}
A model for a single object is that its intrinsic properties (captured by equivalent width) are drawn from a Normal distribution
\begin{equation}
\left(
\begin{matrix}
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
EW_{0, Si}\\ EW_{0, Ca}
\end{matrix}
\right)
,C_{EW}
\right),
\end{equation}
with global parameters $EW_{0, Si}$, $EW_{0, Ca}$, and the independent elements of $C_{EW}$.
The colors, which depend on the intrinsic properties and the extrinsic effect of dust, are modeled as
\begin{equation}
\left(
\begin{matrix}
U-V\\B-V\\V-R\\V-I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k+ E(U-V) \\
c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +k +E(B-V) \\
c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k + E(V-R)\\
c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k +E(V-I)\\
\end{matrix}
\right)
,C_c
\right),
\end{equation}
where there are global parameters $\alpha_X$, $\beta_X$, $c_X$,  and the independent elements of $C_c$,
while each supernova has independent parameters $E(X-V)$ and intrinsic color parameter $k$.

>>>>

\begin{document}

\begin{equation}
\left(
\begin{matrix}
U-V\\B-V\\V-R\\V-I\\EW_{Si, o}\\ EW_{Ca, o}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k  \\
c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +\gamma_1 k  \\
c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k\\
c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right),
\end{equation}

A model for a single object is that its intrinsic properties (captured by equivalent width) are drawn from a Normal distribution
\begin{equation}
\left(
\begin{matrix}
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
EW_{0, Si}\\ EW_{0, Ca}
\end{matrix}
\right)
,C_{EW}
\right),
\end{equation}
with global parameters $EW_{0, Si}$, $EW_{0, Ca}$, and the independent elements of $C_{EW}$.
The colors, which depend on the intrinsic properties and the extrinsic effect of dust, are modeled as
\begin{equation}
\left(
\begin{matrix}
U-V\\B-V\\V-R\\V-I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k+ E(U-V) \\
c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +k +E(B-V) \\
c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k + E(V-R)\\
c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k +E(V-I)\\
\end{matrix}
\right)
,C_c
\right),
\end{equation}
where there are global parameters $\alpha_X$, $\beta_X$, $c_X$,  and the independent elements of $C_c$,
while each supernova has independent parameters $E(X-V)$ and intrinsic color parameter $k$.
